---
title: "p8105_hw1_hy2958"
output: gitinstall.packages("moderndive")_document
date: "2025-09-20"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r setup}
library(moderndive)
library(ggplot2)
library(tidyverse)
```

##problem 1
data import

```{r}
data("early_january_weather")
```

##describe data

```{r}

names(early_january_weather)
str(early_january_weather)
nrow(early_january_weather)
ncol(early_january_weather)
summary(early_january_weather)
```


The data describe the weather condition from January 1st to January 15th in 2013 in EWR.

It contains 15 variables:"origin"     "year"       "month"      "day"  "hour"       "temp"       "dewp"       "humid"     "wind_dir"   "wind_speed" "wind_gust"  "precip"  "pressure"   "visib"      "time_hour", 1 character, 13 numeric and 1 POSIXct.

It contains 358 rows and 15 columns

The mean temperature is 39.58

plot
```{r}
ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) +
  geom_point() +
  labs(x = "Time", y = "Temperature (°F)", color = "Humidity") +
  scale_color_viridis_c()  # Color scale for humidity

ggsave("temp_vs_time_hour.png", width = 8, height = 5, dpi = 300)
```

It reflect that the temperature and humidity had overall increasing trend between January 1st to January 15th in 2013 in EWR.


##problem 2

create dataframe
```{r}
df <- data.frame(
  normal_sample = rnorm(10),
  logical_vector = rnorm(10) > 0,
  character_vector = letters[1:10],
  factor_vector = factor(rep(c("Low", "Medium", "High"), length.out = 10))
)
```

take the mean
```{r}
mean_normal <- mean(pull(df, normal_sample))
mean_logical <- mean(pull(df, logical_vector))
mean_character <- mean(pull(df, character_vector)) #fail
mean_factor <- mean(pull(df, factor_vector)) #fail
```

Only the numerical and logical variable's mean can be calculated. The character and factor variable's mean cannot be calculated.


